---
title: "Alex.Row.20067626.A4"
author: "Alexander Row - 20067626"
date: "03/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Project Info
This assignment uses regex syntax to manipulate organism names to display only the first letter of the genus, followed by a period and keeping the species name in tact. Regex code is used in combination with dplyr.

The following lines of code load the dataset
```{r}
measurement <- read.csv("InputData/Measurements2.csv", header = TRUE)
```

## Create New Column, Arrange Columns, and remove Organism column

Use a dplyr command AND regular expression(s) to add a new column called Sp that shortens the genus name in the Organism column to only the first letter and period. For example: Homo sapiens in the original Organism column becomes H. sapiens in the Sp column. HINT: You can think of the regular expression commands like sub, grep, grepl and gsub as 'functions' that you can use with dplyr commands just like mean(), sd(), and desc() in the Data Science tutorial.

```{r}
measurement <- measurement %>% 
  mutate(Sp = sub("(\\w)\\w+", "\\1.", Organism)) %>%  #select only the first letter and place a period after it 
  select(Sp, Limb.width, Limb.length)  #select and reorder the columns 
measurement
```

## Write out the new data

```{r}
write.csv(measurement, "MeasShort.csv") #write the new data to project folder
```





