---
title: "Assingment3B"
author: "Alexander Row - 20067626"
date: "26/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Project Info

Date: January 26, 2021

This report will manipualte a dataset to exemplify use of dplyr and GitHub. The link to my [GitHub account](https://github.com/settings/profile) with username alexrow15.

##Load Fallopia Dataset
```{r}
Fallopia <- read.csv("InputData/FallopiaData.csv")
```


```{r echo = FALSE}
library(dplyr) #load required packages
```

##Remove Rows with **'Total'** <60
```{r}
X <- filter(Fallopia, Total<60)
head(X)
```

##Reorder and Remove Columns
```{r}
X <- select(Fallopia, Total, Taxon, Scenario, Nutrients)
head(X)
```

## Convert Total from mg to g AND replace Total with TotalG
```{r}
X <- X %>%
  mutate(TotalG = (Total/1000)) %>% 
  select(TotalG, Taxon, Scenario, Nutrients)
head(X)
```

## Write a custom function to manipulate the dataset
```{r}

SummaryStats <- function(column, string){
  if (string == "Average"){
    return(summarise(X, mean = mean(column)))
  } 
  
  if (string == "Sum"){
    return(summarise(X, sum = sum(column)))
  }
  
  if (string == "Observations"){
    return(summarise(X, Observations = length(column)))
  }
  else{
    print("Error Occurred, column name or operation not found")
  }
}
```

## Test the Function

Utilising the function to count the total numer of observations in the "Taxon" column
```{r}
SummaryStats(X$Taxon, "Observations")
```

Utilising the function to calculate the average TotalG for each of the two nutrient Concentrations
```{r}
low <- subset(X, Nutrients =="low")
SummaryStats(low$TotalG, "Average")
```
```{r}
high <- subset(X, Nutrients =="high")
SummaryStats(high$TotalG, "Average")
```

## Write the Wrangled Data to a new output

```{r}
setwd("~/Desktop/Assignment3B/Output")
write.csv(X, "WrangledData.csv")
```





